\chapter{Preface}


This master thesis, written during the spring of 2013 at the Department of Mathematical Sciences and Technology, Norwegian University of Life Sciences, marks the end of my five year study program, Environmental Physics and Renewable Energy. 
The aim of this thesis has been to develop statistical test for some of the main connection algorithms used in neural networks. 

The subject of this thesis is located somewhere in the intersection between the fields of statistics, computer science and neuroscience. I have some basic training in the first two, but the last one was completely new to me before I started this work. That was partly why I chose this subject. It was an opportunity to gain some insight into this exciting field, that is unraveling the mysteries of the human mind, and might come to shape technology in the future. Working on this project has been just as educational and interesting as I had hoped for. 

I would like to thank my supervisor, Hans Ekkehard Plesser, and my co-supervisor, Birgit Kriener, for their guidance along the way, and for always taking the time to answer my questions thoroughly. Our fruitful conversations have been of great help.
I would also like to thank my parents for their unconditional love and support throughout my life, and for cheering for me from the sidelines through this project. Last, but not least, I would like to thank Elina. You have been very supportive, and always patient, even through the most stressful times, when I was glued to my computer for hours on end, unable to tear myself away.


\clearchapter

